Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-08-04 manuscript/manuscript.tex
Continue writing manuscript

\todo{explicar pq los otros campos no los testeamos}

@@

\begin{table}
\caption{
    Description of the synthetic grids where the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height.
}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

\noindent where $A$ = 1 kg/m$^3$ and $b$ = 10$^6$ m.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively.
The results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.

>>>>

@@

The tests were only performed on these three magnitudes because the other components of the gravity gradient and Marussi tensor are equal to zero due to the rotational symmetries of the spherical shell.

\begin{table}
\caption{
    Description of the synthetic grids where the comparison of the numerical model against the analytical solutions for a spherical shell was done. This collection of grids tries to include every possible scenario on which the numerical model can present a different behaviour depending on the size of the grid, its location or its height. Every grid consists in a set of 10$\times$10 points.
}
\label{tab:grids}
\begin{tabular}{lcccc}
    Grid & Size & Lat. extension & Lon. extension & Height \\ \hline
    Pole & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Equator & $1^\circ \times 1^\circ$ & $0^\circ - 1^\circ$ & $0^\circ - 1^\circ$ & 2km \\
    Satellite & $1^\circ \times 1^\circ$ & $89^\circ - 90^\circ$ & $0^\circ - 1^\circ$ & 260km \\
    Big Grid & $30^\circ \times 30^\circ$ & $60^\circ - 90^\circ$ & $0^\circ - 30^\circ$ & 2km \\
\end{tabular}
\end{table}

@@

\noindent where $A$ = 1 kg/m$^3$ and $b$ = 10$^6$ m.
We have also performed this test with a thin and a thick shell of 1 km and 35 km, respectively, and the results can be seen in Figures \ref{fig:D-exp-thin} and \ref{fig:D-exp-thick}.

In the same way we analysed the linear density results, we can summarise that the thin spherical shell presents the more conservative values of the distance-size ratio: $D=1$ for the gravity potential, $D=2$ for its gradient components and $D=8$ for the Marussi tensor components.

Surprisingly both the linear and the exponential density tesseroid models needs the same values of distance-size ratio $D$ in order to assure a good accuracy.
Because the two functions are significantly different we can expect that these values of $D$ are good for a wide variety of density functions.
